``FISTA'' in Banach spaces with adaptive discretisations

### 2022-03-16 paper.tex
Measurable domains

	\begin{definition}\label{def: finite element space}
		Suppose \edit{}{$\norm\cdot_q\lesssim \Norm\cdot$ (i.e. }$\F{U}\subset L^q(\Domain)$\edit{}{)} for some \edit{}{$q\in[1,\infty]$ and }connected, bounded domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{}. We say that \edit{$\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$}{a collection $\F M$} is a \emph{mesh} if 
		$$\edit{\domain_i^k\subset}{\bigcup_{\domain\in\F M}\domain = } \Domain \qquad\text{and} \qquad |\edit{\domain_i^k\cap\domain^k_j}{\domain\cap\domain'}| = 0\qquad \text{for all \edit{$i$ and $j$}{$\domain,\domain'\in\F M,\ \domain\neq\domain'$}.}$$
		\edit{We say that $\tilde{\F{U}}^k\subset \F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\tilde{\var0}\in\tilde{\F{U}}^k$ there exists $\var0_i^k\in\tilde{\F{U}}^k$ such that
		\\$\supp(\var0_i^k)\subset \bar{\domain_i^k}, \qquad \tilde{\var0}(\vec{x}) = \var0^k_i(\vec{x}) \qquad \text{ for a.e. }\vec{x}\in\domain_i^k, \text{ all } i\in\F N.$\\
		We say that the sequence $(\tilde{\F{U}}^k)_{k\in\F N}$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\F{U}}^0\cap L^\infty(\Domain)$ such that for any $\var0_i^k\in\tilde{\F{U}}^k$ with $\supp(\var0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that 
		\\$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \var0_i^k(\vec{x}) = \sum_{j=1}^N\vars2_je_j(\vars0 \vec{x}+\vvars1) \quad \text{ for a.e. }\vec{x}\in\domain_i^k, \quad \supp(e_j(\vars0\cdot+\vvars1))\subset\bar{\domain_i^k}. $\\}{%
		Furthermore, we say a sequence of meshes $(\F M^k)_{k\in\F N}$ is \emph{consistent} if there exists $\domain_0\in\F{M}^0$ such that
		$$ \forall\domain\in\F{M}^k \quad \exists (\vars0_\domain,\vvars1_\domain)\in\R^{d\times d}\times\R^d \quad\text{such that}\quad \vec{x}\in\domain_0\iff \vars0_\domain\vec{x}+\vvars1_\domain\in\domain. $$
		Fix $\meshsize\in(0,1)$, linear subspaces $\tilde{\F{U}}^k\subset\F{H}$, and consistent meshes $\F M^k$. We say that the sequence $(\tilde{\F{U}}^k)_{k\in\F N}$ is an \emph{$\meshsize$-refining sequence of finite element spaces} if there exists $c_{\vars0}>0$ such that:
		$$ \forall (\tilde{\var0},\domain)\in(\tilde{\F{U}}^k,\F{M}^k),\quad \op{det}(\vars0_\domain)\geq c_{\vars0}\meshsize^{kd} \quad\text{and}\quad \exists \var0\in\tilde{\F U}^0 \quad\text{such that}\quad \forall\vec{x}\in\domain_0,\ \var0(\vec{x})=\tilde{\var0}(\vars0_\domain\vec{x}+\vvars1_\domain).$$}
		We say that $(\tilde{\F{U}}^k)_k$ is \emph{of order $p$} if \edit{}{for any $\var0^*\in\argmin_{\var0\in\F U}\op{E}(\var0)$ there exists a sequence $(\tilde{\var2}_k)_{k\in\F N}$ such that}
		\begin{equation}\label{eq: projection of u*}
			\edit{\min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*} \lesssim_{\var0^*} \meshsize^{kp}}{\forall k\in\F N, \qquad\tilde{\var2}_k\in\tilde{\F U}^k  \quad\text{and}\quad \Norm{\tilde{\var2}_k-\var0^*}\lesssim_{\var0^*} \meshsize^{kp}}.
		\end{equation}

>>>>

	\begin{definition}\label{def: finite element space}
		Suppose \edit{}{$\norm\cdot_q\lesssim \Norm\cdot$ (i.e. }$\F{U}\subset L^q(\Domain)$\edit{}{)} for some \edit{}{$q\in[1,\infty]$ and }connected, bounded\edit{}{, measurable} domain $\Domain\subset\R^d$\edit{ with sufficiently smooth boundary}{}. We say that \edit{$\F M^k = \{\domain_1^k,\domain_2^k,\ldots\}$}{a collection $\F M$} is a \emph{mesh} if 
		$$\edit{\domain_i^k\subset}{\bigcup_{\domain\in\F M}\domain = } \Domain \qquad\text{and} \qquad |\edit{\domain_i^k\cap\domain^k_j}{\domain\cap\domain'}| = 0\qquad \text{for all \edit{$i$ and $j$}{$\domain,\domain'\in\F M,\ \domain\neq\domain'$}.}$$
		\edit{We say that $\tilde{\F{U}}^k\subset \F H$ is a \emph{finite element space} if there exists a mesh $\F M^k$ such that for all $\tilde{\var0}\in\tilde{\F{U}}^k$ there exists $\var0_i^k\in\tilde{\F{U}}^k$ such that
		\\$\supp(\var0_i^k)\subset \bar{\domain_i^k}, \qquad \tilde{\var0}(\vec{x}) = \var0^k_i(\vec{x}) \qquad \text{ for a.e. }\vec{x}\in\domain_i^k, \text{ all } i\in\F N.$\\
		We say that the sequence $(\tilde{\F{U}}^k)_{k\in\F N}$ is \emph{$\meshsize$-refining} if there exists a basis $\{e_1, \ldots,e_N\}\subset\tilde{\F{U}}^0\cap L^\infty(\Domain)$ such that for any $\var0_i^k\in\tilde{\F{U}}^k$ with $\supp(\var0_i^k)\subset\domain_i^k$ there exist $\vars0\in\R^{d\times d}$, $\vvars1\in\R^d$, $\vvars2\in\R^N$ such that 
		\\$0<\op{det}(\vars0) \lesssim \meshsize^{-kd}, \quad \var0_i^k(\vec{x}) = \sum_{j=1}^N\vars2_je_j(\vars0 \vec{x}+\vvars1) \quad \text{ for a.e. }\vec{x}\in\domain_i^k, \quad \supp(e_j(\vars0\cdot+\vvars1))\subset\bar{\domain_i^k}. $\\}{%
		Furthermore, we say a sequence of meshes $(\F M^k)_{k\in\F N}$ is \emph{consistent} if there exists $\domain_0\in\F{M}^0$ such that
		$$ \forall\domain\in\F{M}^k \quad \exists (\vars0_\domain,\vvars1_\domain)\in\R^{d\times d}\times\R^d \quad\text{such that}\quad \vec{x}\in\domain_0\iff \vars0_\domain\vec{x}+\vvars1_\domain\in\domain. $$
		Fix $\meshsize\in(0,1)$, linear subspaces $\tilde{\F{U}}^k\subset\F{H}$, and consistent meshes $\F M^k$. We say that the sequence $(\tilde{\F{U}}^k)_{k\in\F N}$ is an \emph{$\meshsize$-refining sequence of finite element spaces} if there exists $c_{\vars0}>0$ such that:
		$$ \forall (\tilde{\var0},\domain)\in(\tilde{\F{U}}^k,\F{M}^k),\quad \op{det}(\vars0_\domain)\geq c_{\vars0}\meshsize^{kd} \quad\text{and}\quad \exists \var0\in\tilde{\F U}^0 \quad\text{such that}\quad \forall\vec{x}\in\domain_0,\ \var0(\vec{x})=\tilde{\var0}(\vars0_\domain\vec{x}+\vvars1_\domain).$$}
		We say that $(\tilde{\F{U}}^k)_k$ is \emph{of order $p$} if \edit{}{for any $\var0^*\in\argmin_{\var0\in\F U}\op{E}(\var0)$ there exists a sequence $(\tilde{\var2}_k)_{k\in\F N}$ such that}
		\begin{equation}\label{eq: projection of u*}
			\edit{\min_{\var2\in\tilde{\F{U}}^k}\Norm{\var2-\var0^*} \lesssim_{\var0^*} \meshsize^{kp}}{\forall k\in\F N, \qquad\tilde{\var2}_k\in\tilde{\F U}^k  \quad\text{and}\quad \Norm{\tilde{\var2}_k-\var0^*}\lesssim_{\var0^*} \meshsize^{kp}}.
		\end{equation}
